Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs

### 2014-06-26 Referee2_Response.tex

\begin{itemize}
\item[] \textit{3, 11: ``solution; and''}
\end{itemize}

\noi
Done.
\medskip

\begin{itemize}
\item[] \textit{3, 24 (and elsewhere): ``Lagrangian, or'' (comma after penultimate entry in a conjunctive list)}
\end{itemize}

\noi
Done.  
We went through the paper and added commas before `and' and `or' in a list of items with three or more items.
\medskip

@@

\begin{itemize}
\item[] \textit{3, 53: ``The sample variance of these estimators is used to form confidence intervals for the optimality gap (we further review MRP in \S 2.2).''}
\end{itemize}

\noi
Done. 
\medskip

\begin{itemize}
\item[] \textit{4, 5 (and elsewhere): ``see, e.g., Bertocchi et al. [2000]; \ldots ''}
\end{itemize}

\noi
We put a comma after `see'; however, we still kept the same referencing style `[Bertocchi et al., 2000; \ldots]' as this sentence refers to the papers and not directly to the authors. 
We also went through the paper to make sure all `see, e.g.,' have the appropriate commas.
\medskip

@@

\begin{itemize}
\item[] \textit{4, 54 (and elsewhere): When you refer to ``variable amounts of overlap'', that is really nothing new. Certainly, any overlapping estimator will have end effects in which the overlap amounts differ from those in the ``middle'' region of the data.}
\end{itemize}

\noi
You are right.
We meant to say that the degree of overlap is parametrized and this parameter can be chosen by the user. 
We reworded this sentence to reflect this. 
xxxx  We also \ldots (I think we should write more about our conclusions and our recommendation based on our new findings here) xxxx
\medskip

\begin{itemize}
\item[] \textit{4, 57 (and elsewhere): ``classical case'' refers to nonoverlapping batch means, right?}
\end{itemize}

\noi
No; by `classical case', we meant the use of overlapping batches in simulation output analysis (as opposed to the assessment of solution quality in stochastic programming). 
We reworded this sentence to make it clear. 
Please note that based on your earlier comments, we reworded this sentence to avoid using the term `variance reduction'. 
We also went through the paper and removed several uses of the word `classical' that referred to nonoverlapping batches to reduce ambiguity.
%(as these were referring to nonoverlapping batches). 
%In the current version of the paper, `classical case' is used to only indicate  the use of overlapping batches in simulation output analysis. 
\medskip

@@

\begin{itemize}
\item[] \textit{5, 12: Does $\sigma^2$ refer to the marginal variance or the ``variance parameter'' (sum of the covariances at all lags)?}
\end{itemize}

\noi
Variance parameter. 
xxx We revised this section to clarify this point. 
\medskip

@@

\begin{itemize}
\item[] \textit{5, 14: ``realization of the univariate stochastic''}
\end{itemize}

\noi
Done.  
\medskip

\begin{itemize}
\item[] \textit{5, 35 (and elsewhere): Careful! This isn't quite the sample variance! This is actually the sample variance multiplied by $m/n$.}
\end{itemize}

\noi
Thanks for catching this. 
We corrected this sentence. 
Please note that we broke this sentence into two to avoid long sentences and to improve exposition. 
We also checked for other uses of the term `sample variance' throughout the paper and corrected these as needed.
Thank you.  
\medskip

@@

\begin{itemize}
\item[] \textit{5, 43: You could have introduced the notation ``CI'' earlier.}
\end{itemize}

\noi
You are right. 
We now introduce this abbreviation the first time we use the term `confidence interval' in the introduction. 
From this point on, we use the abbreviated form `CI' throughout the paper, except for the title of Section 4.5 (Asymptotic Validity of the Confidence Intervals). 
\medskip

@@

\begin{itemize}
\item[] \textit{6, 13: ``corresponding overlapping batch means''}
\end{itemize}

\noi
Done. 
\medskip

\begin{itemize}
\item[] \textit{6, 29: Note that you use ``Note that'' too often.}
\end{itemize}

\noi
We went through the paper and removed most of the ``note that'' phrases. 
We decided to leave a couple as is (mainly as ``notice that'') because they highlight important characteristics.  
\medskip

@@

\begin{itemize}
\item[] \textit{13, 12 (and elsewhere): I may have missed this, but has the notation $\sigma_{\hat{x}}$ been established yet? 
In any case, some of the verbiage in this paragraph is a bit repetitive.}
\end{itemize}

\noi
xxx  
\medskip

\begin{itemize}
\item[] \textit{13, 44: Is the expression for d.f. too big?}
\end{itemize}

\noi
We now denote it as `dt' to represent the whole denominator term. 
\medskip

@@

\begin{itemize}
\item[] \textit{15, 25: Do you discuss $t_{d_l,\alpha}$ at all in Theorem 3?}
\end{itemize}

\noi
No, we did not.   
We added explanations in the proof Theorem 3, discussing how $t_{d_l,\alpha}$ factors in the proof. 
\medskip

\begin{itemize}
\item[] \textit{18: Your figures are very difficult to read, even with the pdf file.}
\end{itemize}

\noi
We split these two figures into three and enlarged each graph. 
We also enlarged the legends in these graphs to improve readability.
All the new graphs added to the paper in Section 5.4 (Computational Efficiency) are also larger, with legible legends. 
\medskip
